Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2024-02-29 doc/manuscript/SI_tables.Rmd
finalize SI tables

---
title: ''
output: 
    pdf_document
bibliography: references.bib
csl: new-phytologist.csl

@@

**`r table_ForCchanges`. Updates to ForC field implemented between releases of v3.0 and v4.0.** 
```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE, message = FALSE}
library (readr)
urlfile="https://raw.githubusercontent.com/forc-db/ForC/master/database_management_records/record_of_changes.csv"
record_of_changes <-read_csv(url(urlfile))
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")
record_of_changes <- record_of_changes[c(1:5)] #include all fields but date of change
#record_of_changes<- record_of_changes[which(!grep("housekeeping",record_of_changes$Motivation)) , c(1:5)]  #trying to exclude rows for which Motivation = "housekeeping", but this is not working
record_of_changes[is.na(record_of_changes)]<- "" #replace NAs with blanks

library(knitr)
library(kableExtra)
knitr::kable(record_of_changes, format = "latex",
             longtable = TRUE) %>%
  kableExtra::kable_styling(full_width = TRUE, latex_options = c("repeat_header")) %>%
  kable_styling(font_size = 8) %>%
  row_spec(0, bold = TRUE)
```

@@

**`r table_ForCfieldmapping`. Mapping of ForC fields to EFDB.** Details documented in the public GitHub repository associated with the project, IPCC-EFDB-integration repository within the ForC-db organization (file *ForC-EFDB_mapping.csv* available at [https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv](https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv)). 
```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)

ForC_variables_included <- read.csv("figures_tables/ForC_fields_included.csv")
names(ForC_variables_included) <- stringr::str_replace_all(names(ForC_variables_included), "\\.", " ")
column_names <- names(ForC_variables_included) # Define column names
column_names[5] <- "Required*" # Add asterisk for footnote
names(ForC_variables_included) <- column_names# Set column names of the matrix
ForC_variables_included <- ForC_variables_included[c(1:5)]

knitr::kable(ForC_variables_included, format = "latex",
             longtable = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(font_size = 8) %>%
kableExtra::kable_styling(full_width = TRUE, latex_options = c("repeat_header", "hold position"))

>>>>

---
title: ''
output: 
    #pdf_document
    bookdown::word_document2: 
      reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
bibliography: references.bib
csl: new-phytologist.csl

@@

**`r table_ForCchanges`. Updates to ForC fields implemented between releases of v3.0 and v4.0.** 
```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE, message = FALSE}
library (readr)
urlfile="https://raw.githubusercontent.com/forc-db/ForC/master/database_management_records/record_of_changes.csv"
record_of_changes <-read_csv(url(urlfile))
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")
record_of_changes <- record_of_changes[c(1:5)] #include all fields but date of change
record_of_changes <- record_of_changes[!grepl("housekeeping", record_of_changes$Motivation, ignore.case = TRUE), c(1:5)]
record_of_changes[is.na(record_of_changes)]<- "" #replace NAs with blanks

library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 8) # set font
ft <- flextable(record_of_changes)
ft <- autofit(ft)
ft <- width(ft, 1, width = 1)
ft <- width(ft, 2:5, width = 1.5)
ft

@@

**`r table_ForCfieldmapping`. Mapping of ForC fields to EFDB.** Details documented in the public GitHub repository associated with the project, IPCC-EFDB-integration repository within the ForC-db organization (file *ForC-EFDB_mapping.csv* available at [https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv](https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv)). 
```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}
library(readr)
library(stringr)
library(flextable)

# Read the data
ForC_variables_included <- read.csv("figures_tables/ForC_fields_included.csv")

# Fix column names
names(ForC_variables_included) <- stringr::str_replace_all(names(ForC_variables_included), "\\.", " ")
column_names <- names(ForC_variables_included) # Define column names
column_names[5] <- "Required*" # Add asterisk for footnote
names(ForC_variables_included) <- column_names# Set column names of the matrix

# Subset to the first 5 columns
ForC_variables_included <- ForC_variables_included[c(1:5)]

# Create flextable object
ft <- flextable(ForC_variables_included)
ft <- autofit(ft)
ft <- width(ft, 1, width = 1)
ft <- width(ft, 2:5, width = 1.5)

# Apply styling
#ft <- ft %>%
#  bold(part = "header") %>%
#  fontsize(size = 8)

ft
